An Algorithm for Searching Evolving Graphs in Linear Algebraic Language

### 2016-01-22 paper.tex
update implementation section

To study evolving graphs and experiment with various graph types, we have developed EvolvingGraphs.jl  \cite{zhang15}, a software package in the Julia language \cite{bkse12} for the creation, manipulation, and study of dynamic networks.
Julia is a high-level, high-performance dynamic programming language for technical
computing. When we implement EvolvingGraphs.jl, we make particular use of
the parameterizable type system and multiple dispatch in Julia.
We define a data type  \texttt{MatrixList}, which represents an evolving graph
as a sequence of sparse matrices stored in compressed sparse column (CSC) format.
Many basic graph functions are defined for \texttt{MatrixList}, including
retrieving nodes, time stamps, and matrices.

>>>>

To study evolving graphs and experiment with various graph types, we have developed EvolvingGraphs.jl  \cite{zhang15}, a software package for the creation, manipulation, and study of evolving graphs written in Julia \cite{bkse12}. The implementation of the evolving-graph BFS is 
available online at 
\begin{center}
\url{https://github.com/weijianzhang/EvolvingGraphs.jl}.
\end{center}
%Julia is a high-level, high-performance dynamic programming language for technical
%computing. 
% We make particular use of
% the parameterizable type system and multiple dispatch in Julia.
 \texttt{MatrixList}, a data type in EvolvingGraphs.jl,  represents an evolving graph
as a sequence of sparse matrices stored in compressed sparse column (CSC) format.
Many basic graph functions are implemented for \texttt{MatrixList}.
